### 2018-04-28 FrascatiPlot/Paper/NucleiB2.tex
adding a link to a summary of hyper-triton paper

>>>>

For the table: there seems to be a nice summary here (including that the hyper-triton is spin 1/2):
https://books.google.fr/books?id=utBKDwAAQBAJ&pg=PA56&lpg=PA56&dq=spin+of+hypertriton&source=bl&ots=x-wqVWSIpJ&sig=k2tZUsruf2M5o-slqOp0Q9v-PCI&hl=de&sa=X&ved=0ahUKEwj1-NOo4t3aAhUCU1AKHbjVCAoQ6AEIczAJ#v=onepage&q=spin%20of%20hypertriton&f=false
Properties And Interactions Of Hyperons - Proceedings Of U.s.-japan Seminar
herausgegeben von Barnes Peter D,Nakai K,Gibson Benjamin F
